On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-27 paper/paper.tex
Added recursion example

In the technique presented here, we do not need to allocate thunks or closures.
We actually do not to use higher-order functions at all in this tail recursion
representation.

In the \ttt{E} type, this is used to represent tail recursion by
the following constructors:

@@

>>>>

In the technique presented here, we do not need to allocate thunks or closures.
We actually do not need to use higher-order functions at all in this tail recursion
representation.

In the \ttt{E} type of our DSL, these types of data structures are used to represent tail 
recursion by using the following constructors.

@@

The process of transforming a tail recursive function in the DSL to a 
representation which could be passed into the C backend and used
to generate a traditional iterative loop goes as follows.

Starting with the tail recursive function  \ttt{isEven}:

\begin{lstlisting}
isEven :: Int -> Bool
isEven x =
    case x == 0 of
      True -> True
      False ->
        case x == 1 of
          True -> False
          False -> isEven (x - 2)
\end{lstlisting}

We translate this to the expression language, and then apply two of
the constructors we have defined.  The first of these is an initial 
\ttt{DoneExp} which we then wrap with a \ttt{TailRec} to provide the
representation of the iteration execution:

\begin{lstlisting}
isEven' :: E Int -> E (Int -> Bool)
isEven' x =
  TailRec ( DoneExp (
    IfThenElseExp (Equal x (rep 0))
      TrueExp
      (IfThenElseExp (Equal x (rep 1))
        FalseExp
        (IsEven' (Sub x (rep 2))))
\end{lstlisting}

The transformation then proceeds by pushing the DoneExp constructor through
the conditionals, and the recursive call is transformed into a StepExp constructor.
This leaves us the the transformed example:

\begin{lstlisting}
isEven'' :: E Int -> E (Int -> Bool)
isEven'' x =
  TailRec (
    IfThenElseExp (Equal x (rep 0))
      (DoneExp TrueExp)
      (IfThenElseExp (Equal x (rep 1))
        (DoneExp FalseExp)
        (StepExp (Sub x (rep 2))))
\end{lstlisting}
